The Exoplanet Orbit Database 2, 2014 updates

### 2014-03-15 draft/ms.tex
Proofread and revisions from sec 1 through sec 2.1.

% Recent development in exoplanet discoveries
Since the launch of NASA's \kepler\ mission \citep{Borucki2010}, the
number of confirmed exoplanets has increased from about 300 to over
1490 as of March 2014 (exoplanets.org). \kepler\ contributed to a vast
majority of these new discoveries ($> 800$) while providing an
additional sample of over 3000 exoplanet candidates(\kepler\ Objects
of Interest, KOIs; e.g.~\citealt{Batalha2013}). The transit method has
surpassed the radial velocity (RV) method and become the most fruitful
mean for detecting exoplanets. Meanwhile, great promises lie within
the new and future exoplanet surveys and instruments with direct
imaging (e.g., the Gemini Planet Imager, GPI,
\citealt{Macintosh2014}) and microlensing (e.g., the Wide-Field
InfraRed Survey Telescope, WFIRST, \citealt{Green2012}), while the
fronts of RV and transit exoplanet searches keep expanding (e.g., the
MINiature Exoplanet RV Array, MINERVA, \citealt{Wright2014}; and the
Transiting Exoplanet Survey Satellit, TESS, \citealt{Ricker2010}).

% The business of tracking planet discoveries and EOD
This paper describes the continuing efforts since \cite{Butler2006}
and \cite{Wright2011} to maintain the Exoplanet Orbit Database (EOD)
and the Exoplanets Data Explorer (EDE) to keep track of the exoplanet
discoveries and catalog their orbital parameters and host star
properties. There are also other entities devoted to this effort,
including the Extrasolar Planets Encyclopaedia\footnote{See
  \url{http://exoplanet.eu}.}  \citep{Schneider2011}, the NASA
Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}. As described in \cite{Wright2011}, the EOD is
dedicated to cataloging all \emph{robustly-detected} exoplanets with
\emph{well-determined} orbital parameters published in
\emph{peer-reviewed} literature.

@@

% updates on EOD and the website
Since \cite{Wright2011}, the EOD has expanded its scope and we now do
not require the host star of an exoplanet to be a normal star (e.g.,
exoplanets around pulsars are now included). It has also ingested more
parameters of the exoplanet systems and host stars, and some
parameters are revised or deleted. We describe the updates with the
EOD in Section~\ref{sec:update}. We also describe the updates to the
hosting website, exoplanets.org. The EDE at exoplanets.org has
expanded its scope and now includes the \kepler\ exoplanet candidates
(KOIs). We describe these changes in Section~\ref{sec:kepler}. The
website has also gone through major back-end changes since
\cite{Wright2011}, which is described in Section~\ref{sec:website}.

@@

The scope of the EOD has not been changed much but there were two
major changes in the EOD. Previously, we only included exoplanets
orbiting the `normal stars', but now we are not limiting the type of
the host star (e.g. we included exoplanets orbiting neutron
stars). Furthermore, we only had exoplanets that were discovered by RV
and transit but as more exoplanets are discovered by various methods
such as timing are now in the EOD. For the future, exoplanets
discovered by other methods with good orbital parameters may also be
included in the EOD.

The rest of the criteria remain unchanged. We still require the
planets to be smaller than 24 \mjup\ and with robust detection (though
not strictly quantitative; see \citealt{Wright2011}).

The purpose of the EOD has not changed; we aim to provide the readers
with comprehensive database for exoplanets that are discovered
up-to-date. However, we do not report \textit{all} the announced
exoplanets as we are not trying to do ``an encyclopedic presentation
of every claimed detection of an exoplanet" \citep{Wright2011}.

We only describe new additions and revised fields here, but list all
fields in Table~\ref{tab:par}. We divide the fields into categories in
consistency with the individual planet page on
exoplanets.org. Figure~\ref{fig:individual} is an example of
individual planet page. Some fields are not explicitly included on the
page (e.g., the URLs), but are explicitly listed in the downloadable
{\tt .csv} file.\footnote{At
  \url{http://exoplanets.org/csv-files/exoplanets.csv}.} Though we
focus on EOD in this section, the fields apply to all planets on
exoplanets.org. For the definition of orbital elements see
\cite{Wright2013} .
%------------------------------------------------------------------------------
\subsection{Discovery and References}\label{sec:disc}

We report general information of when, by whom and how the planets
were discovered and provide the references. We describe the added
fields since \cite{Wright2011} below.

{\bf DISCMETH} field previously reported the method of discovery,
which was either radial velocity or transit. We have replaced DISCMETH
with {\bf PLANETDISCMETH} and \mbox{{\bf STARDISCMETH}} to better
report how the host star and the planet are detected. PLANETDISCMETH
and STARDISCMETH are the fields that report the discovery methods for
the planet and the first planet around the host star,
respectively. Furthermore, they now have values of one of the
following: radial velocity, transit, imaging, microlensing, timing, or
astrometry.

{\bf MONTH} field reports the month in integer when the peer-reviewed
paper is accepted to the ApJ.

{\bf KEPID} stands for KEPler ID which is the integer number assigned
for a Kepler host star. KEPID is only available for the unconfirmed
KOI which we import directly from the Exoplanet Archive. Therefore,
none of the EOD planets and the confirmed Kepler planets has KEPID.

{\bf KOI} stands for Kepler Objects of Interest which is a star with
transit signals detected by \kepler\ but have not been confirmed to
due to exoplanets. The KOI field contains a floating point number that
consist of a whole number designated to the host star followed by a
decimal number denoting a candidate planet. For example, KOI 102 is a
star suspected to host two exoplanets and KOI 102.01 is the inner
planet candidate and KOI 102.02 is the outer one. Once a candidate is
confirmed, the NAME field of the planet is replaced by the official
\kepler\ ID ('Kepler' followed by a hyphen, an integer and a
letter). The KOI number is used as OTHERNAME. None of the KOIs are in
the EOD and for more information see Section~\ref{sec:kepler}.

\begin{comment}
\textit {Sharon: you need to say what KOI stores. When writing each
  field, keep in mind you need to cover the following so that the
  reader will completely understand: (1) what the field stands for
  (e.g., in case of an abbreviation like KOI); (2) what the field
  physically means, like `KOI' means planet candidates that have
  transit signals as detected by \kepler\ but have not been confirmed,
  and make sure to be thorough at what you say -- sometimes things are
  not that obvious to an outsider reader, e.g., think if a cosmologist
  would understand what you're saying when reading it; (3) what the
  field actually contains, e.g. KOI contains the KOI number designated
  by the \kepler\ team (right?), it is a floating point number, and
  sometimes maybe even worth giving an example, e.g. KOI 30.1 or
  something...; (4) why we added this new field, if this information
  is helpful, or if it's a revised field since \cite{Wright2011}, what
  is changed. Also, use \kepler\ (which is a defined symbol in our
  ms.tex file), instead of typing out Kepler, since you need italic.
  Don't be afraid to write more! Being concise is important, but it's
  always easier to trim down things than to add things on, especially
  for a documentation type of paper like this. Let's be thorough at
  first, then try to reach optimal conciseness.}
 \end{comment}

%KDE: obselete field! Detele from the table.

{\bf EOD} is a flag which indicates whether an exoplanet has
well-characterized orbital parameters (e.g. period (PER)). EOD equals
1 means the exoplanet is in the EOD. We added this field because
exoplanets.org now also includes robustly discovered planets that do
not have well-characterized orbits, and also \kepler\ planet
candidates (see Section~\ref{sec:kepler} for more details).

{\bf MICROLENSING, IMAGING, TIMING and ASTROMETRY} are flags which
indicate that a planet detected via theses methods. For example,
MICROLENSING $=$ 1 means the planet is detected by a microlensing
event. However, we require the detection to be robust, as determined
by the QUAlity Control Board of the Exoplanet Database, QUACBED.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Future Work}\label{sec:conclusion}

>>>>

% Recent development in exoplanet discoveries
Since the launch of NASA's \kepler\ mission \citep{Borucki2010}, the
number of confirmed exoplanets has increased from about 300 to over
1490 as of March 2014 (exoplanets.org). \kepler\ contributed to a vast
majority of these new discoveries ($> 800$) while providing an
additional sample of over 3000 exoplanet candidates (\kepler\ Objects
of Interest, KOIs; e.g.~\citealt{Batalha2013}). The transit method has
surpassed the radial velocity (RV) method and become the most fruitful
mean for detecting exoplanets. Meanwhile, great promises lie within
the new and future exoplanet surveys and instruments with direct
imaging (e.g., the Gemini Planet Imager, GPI,
\citealt{Macintosh2014}) and microlensing (e.g., the Wide-Field
InfraRed Survey Telescope, WFIRST, \citealt{Green2012}), while the
fronts of RV and transit exoplanet searches keep expanding (e.g., the
MINiature Exoplanet RV Array, MINERVA, \citealt{Wright2014}; and the
Transiting Exoplanet Survey Satellit, TESS, \citealt{Ricker2010}).

% The business of tracking planet discoveries and EOD
This paper describes the continuing efforts since \cite{Butler2006}
and \cite{Wright2011} to maintain the Exoplanet Orbit Database (EOD)
and the Exoplanets Data Explorer (EDE) to keep track of the exoplanet
discoveries and to catalog their orbital parameters and host star
properties. There are also other entities devoted to this effort,
including the Extrasolar Planets Encyclopaedia\footnote{See
  \url{http://exoplanet.eu}.}  \citep{Schneider2011} and the NASA
Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}. As described in \cite{Wright2011}, the EOD is
dedicated to cataloging all \emph{robustly-detected} exoplanets with
\emph{well-determined} orbital parameters published in
\emph{peer-reviewed} literature.

@@

% updates on EOD and the website
Since \cite{Wright2011}, the EOD has expanded its scope: we now do
not require the host star of an exoplanet to be a normal star (e.g.,
exoplanets around pulsars are now included). It has also ingested more
parameters describing the exoplanet systems and their host stars, and some
parameters are revised or deleted. We describe the updates with the
EOD in Section~\ref{sec:update}. The EDE at exoplanets.org has also
expanded its scope and now includes the \kepler\ exoplanet candidates
(KOIs). We describe these changes in Section~\ref{sec:kepler}. The
website exoplanets.org has gone through major back-end changes since
\cite{Wright2011}, which is described in Section~\ref{sec:website}. We
summarize the updates and possible future improvements in
Section~\ref{sec:summary}.

@@

The scope of the EOD has expanded, and there are two major changes
from what was described in \cite{Wright2011}. Previously, we only
included exoplanets orbiting the ``normal stars", but now we are not
limiting the type of host stars (e.g. we included exoplanets orbiting
neutron stars). Furthermore, in \cite{Wright2011}, we only had
exoplanets that were discovered by the RV and transit methods in the
EOD, but now we also have planets discovered via timing. For the
future, exoplanets discovered by any other methods with robust
detections and good orbital parameters will also be included in the
EOD.

The rest of the selection criteria for the EOD remain unchanged. We
still require the planets to be smaller than 24 \mjup\ and to have
robust detections and well-determined orbits (though these are not
strictly quantitative; see Section~2 of \citealt{Wright2011}).

The purpose of the EOD has not changed: we aim to provide the readers
with a comprehensive, reliable, and up-to-date database of exoplanets
with good orbital parameters and host star properties. We do not
report \textit{all} the announced exoplanets as we are not trying to
do ``an encyclopedic presentation of every claimed detection of an
exoplanet" \citep{Wright2011}.

In the following subsections, we describe the newly added and revised
fields since \cite{Wright2011}, but list all fields in
Table~\ref{tab:par}. We divide the fields into categories in
consistency with the individual planet page on
exoplanets.org. Figure~\ref{fig:individual} is an example of
individual planet page. Some fields are not explicitly tabulated on
the page (e.g., the URLs), but are explicitly listed in the
downloadable {\tt .csv} file (see Section~\ref{sec:intro}). Though we
focus on the EOD in this section, the fields apply to all planets on
exoplanets.org. We follow the definition of orbital elements in
\cite{Wright2013} unless indicated otherwise.

%------------------------------------------------------------------------------
\subsection{Discovery and References}\label{sec:disc}

We report general information of when, by whom and how the planets
were discovered and provide the references. We describe the added or
revised fields since \cite{Wright2011} below.

{\bf DISCMETH} field previously reported the method of discovery,
which was either radial velocity or transit. We have replaced DISCMETH
with {\bf PLANETDISCMETH} and \mbox{{\bf STARDISCMETH}} to better
report how exoplanet systems and individual exoplanets are first
discovered. PLANETDISCMETH reports the discovery method for the
planet, wihle STARDISCMETH reports the discovery method for the first
discovered planet around the host star. Furthermore, they are stored
in string formats and have values of one of the following: RV,
Transit, Imaging, Microlensing, Timing, or Astrometry.

{\bf MONTH} field reports the month in integer of when the
peer-reviewed paper is accepted by the journal.

{\bf KEPID} stands for KEPler ID, which is the integer number assigned
for a Kepler host star. KEPID is only available for the unconfirmed
KOI which we import directly from the Exoplanet Archive. Therefore,
none of the EOD planets and the confirmed Kepler planets has KEPID.

{\bf KOI} stands for Kepler Objects of Interest, which is an object
with transit signals detected by \kepler\ but have not been confirmed
to be due to exoplanets. The KOI field contains a floating point
number that consist of a whole number designated to the host star
followed by a decimal number denoting a candidate planet. For example,
KOI 102 is a star suspected to host two exoplanets, and KOI 102.01 is
the inner planet candidate and KOI 102.02 is the outer one. Once a
candidate is confirmed, the NAME field of the planet is replaced by
the official \kepler\ ID (``Kepler" followed by a hyphen, an integer
and an lower case letter). The KOI number is then used as
OTHERNAME. None of the KOIs are in the EOD. For more information, see
Section~\ref{sec:kepler}.

{\bf EOD} is a flag which indicates whether an exoplanet is included
in the EOD for having robust detection and well-characterized orbital
parameters such as the orbital period (PER). EOD equals 1 means the
exoplanet is in the EOD. We added this field because exoplanets.org
now also includes robustly discovered planets that do not have
well-characterized orbits, and also \kepler\ planet candidates (see
Section~\ref{sec:kepler} for more details).

{\bf MICROLENSING, IMAGING, TIMING and ASTROMETRY} are flags which
indicate that a planet detected via theses methods. For example,
MICROLENSING $=$ 1 means the planet is detected in a microlensing
event. However, we require the detection to be robust, as determined
by the QUAlity Control Board of the Exoplanet Database, QUACBED (see
Section~\ref{sec:kepler}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Future Work}\label{sec:summary}
